### 2020-06-17 docs/LaTex/Paper.tex
Finises gateway subsection

So generating a pair of keys and configuring properly the ssh access; it will probably be necessary to paste the \cmd{*.pub} key content into \cmd{~/.ssh/authorized\_keys} file (located in the local folder in the Raspberry Pi); and give it the right permissions (\cmd{700}), after this the reader should be able to connect through ssh service.

@@

Then it would be necessary to install the GPIO access library from Raspberry repositories, \cmd{sudo apt install wiringpi}. After this, the reader will be in position to clone the controller from the github repository \cite{Dragino_DualChannelController_Rpi}

@@

These last two instructions show information about service status and \cmd{dual\_chan\_pkt\_fwd} status

>>>>

So generating a pair of keys and configuring properly the ssh access;\footnote{The reader will probably need to figure out the Raspberry IP in their local network, by other hand, inside a local network will not be necessary specify any port for ssh, though it usually is the 22 by default.} it will probably be necessary to paste the \cmd{*.pub} key content into \cmd{~/.ssh/authorized\_keys} file (located in the local folder in the Raspberry Pi); and give it the right permissions (\cmd{700}), after this the reader should be able to connect through ssh service.

@@

Then it would be necessary to install the GPIO access library from Raspberry repositories, so performing \cmd{sudo\, apt\, install\, wiringpi}. After this, the reader will be in position to clone the controller from the github repository \cite{Dragino_DualChannelController_Rpi}

@@

These last two instructions show information about service status and \cmd{dual\_chan\_pkt\_fwd} status; in the following picture it can be seen the service active (running)

\begin{figure}[ht]
  \centering
  \includegraphics[width=.82\textwidth]{../pictures/pkt_fwd-service.png}
  \caption{systemd showing the \cmd{dual\_chan\_pkt\_fwd.service} status; it is active and running.}
  \label{fig:dual_chan_pkt_fwd-status}
\end{figure}

As can be seen, this service was modified in order to reach properly the \cmd{dual\_chan\_pkt\_fwd} binary, which is not located in \cmd{/home/pi/dual\_chan\_pkt\_fwd/dual\_chan\_pkt\_fwd} (the default location defined for the binary in the \href{https://github.com/dragino/dual_chan_pkt_fwd/blob/master/dual_chan_pkt_fwd.service#L9}{GitHub repository}); mainly because the user is not called \cmd{pi} anymore but \cmd{wyre}, the path needs to be modified to that path containing the binary (\cmd{/home/wyre/TFG/LoRa/dual\_chan\_pkt\_fwd/dual\_chan\_pkt\_fwd})\footnote{This is a personal setup and is completely optional, the reader can choose their own path or even setup as suggested with \cmd{pi} user.}

After this the Raspberry Pi is ready to forward LoRa packets to the \href{https://github.com/dragino/dual_chan_pkt_fwd/blob/master/global_conf.json#L33}{specified server at line 33 in \cmd{global\_conf.json}}. Besides, the reader will be able to manage the Raspberry Pi through ssh service, so the Raspberry only precises any kind of internet access point and electrical power supply.
